A Case Study in Preserving a High Energy Physics Application

### 2014-03-13 paper.tex
add the execution time on virtual machines

The first three solutions are all directly verified on the machine the original
author used to execute the experiment, which is convenient but involves access
authority problem. Solution 4 is verified on the original machine and on one virtual machine.
To compare the execution time and data size of Solution 4
with Solution 2, the package generated on the original machine is utilized to
rerun the experiment on the original machine. This choice avoids the impact of
different CPUs of the original machine and the new machine to repeat the
experiment. To completely verify the correctness of Solution 4, one virtual
machine sharing the same kernel version with the original machine is deployed.
Then the necessary software environment is configured on the virtual machine,
and the package together with the map file are copied onto it, and the
experiment is repeated on the virtual machine.

@@

>>>>

The first three solutions are all directly verified on the machine the original
author used to execute the experiment, which is convenient but involves access
authority problem. Solution 4 is verified on the original machine and on one virtual machine.
To compare the execution time and data size of Solution 4
with Solution 2, the package generated on the original machine is utilized to
rerun the experiment on the original machine. This choice avoids the impact of
different CPUs of the original machine and the new machine to repeat the
experiment.

To completely verify the correctness of Solution 4, one virtual
machine sharing the same kernel version with the original machine is deployed.
Then the necessary software environment is configured on the virtual machine,
and the package is copied onto it, and the
experiment is repeated on the virtual machine.

One virtual machine from amazon EC2 is used to verify the reproducibility of the experiment. Table~\ref{table:config-vm} illustrates the configuration of the original machine and each virtual machine. 
All the machines adopt x86\_64 hardware platform and linux OS.
Both the local VM and EC2 VM repeat the experiment with the help of the package generated on the original machine successfully.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|r|r|}
    \hline
    Machine & Kernel & Distro & CPU & Mem\\ 
    Type & Version & Version & Cores & (GB)\\ \hline
    earth  & 2.6.18-371.4.1.el5 & RedHat 5.10 & 64 & 125 \\ \hline 
    local VM& 2.6.18-371.4.1.el5 & CentOS 5.10 & 4 & 2 \\ \hline
    EC2 VM& 2.6.18-348.el5xen & RedHat 5.9 & 16 & 60.5 \\ \hline
    \end{tabular}
    \caption{Configuration of Different Machines}
    \label{table:config-vm}
\end{table}

The configuration of earth machine. The configuration of our virtual machine. The configuration of amazon ec2.
each vm: data download time; untar time; script execution time;

@@

\subsection{Excution Time on Different Machines}
Table~\ref{table:time-vm} shows the execution time of the experiment on different machines - the original machine, local VM and EC2 VM. 
Each machine utilizes the package generated on the original machine (i.e. earth) to repeat the experiment.
The execution time on one machine greatly depends on its hardware configuration, which is shown in Table~\ref{table:config-vm}.

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Machine Type & Execution Time \\ \hline
    earth & 13min 4s \\ \hline
    EC2 VM & 13min 30s\\ \hline
    local VM & 21min 38s \\ \hline
    \end{tabular}
    \caption{Execution Time on Different Machines}
    \label{table:time-vm}
\end{table}
